Tracing the Stellar Halo of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam

### 2017-04-18 draft/paper1.tex
Minor changes; new references

% Package Settings
\hypersetup{colorlinks=true,
            citecolor=cyan,
            linkcolor=cyan,
            filecolor=magenta,      
            urlcolor=cyan}
\urlstyle{same}

@@

% Commenting:
\newcommand{\xxx}[1]{\textcolor{red}{\textbf{XXX}}}
\newcommand{\todo}[1]{\textcolor{red}{\textbf{TODO:~#1}}}
\newcommand{\plan}[1]{\textcolor{cyan}{#1}}
\newcommand{\addref}{{\textcolor{red}{REF}}}
\newcommand{\note}[2]{\textcolor{blue}{\textbf{[Comment (#1): #2]}}}
\newcommand{\song}[1]{\textcolor{magenta}{\textbf{[Song: #1]}}}
\newcommand{\alexie}[1]{\textcolor{blue}{\textbf{[Alexie: #1]}}}
\newcommand{\jenny}[1]{\textcolor{Bittersweet}{\textbf{[Jenny: #1]}}}
\newcommand{\kevin}[1]{\textcolor{green}{\textbf{[Kevin: #1]}}}
\newcommand{\update}[1]{\textcolor{OliveGreen}{#1}}
%\newcommand{\update}[1]{#1}

@@

    For the remainder of this paper, we will use \mtot{} as a proxy of ``total'' 
    stellar mass.

    In Appendix~\ref{app:sedasic}, we briefly summarize the basic statistics of 
    the sample using our estimates of \mtot{} and \minn{}.
    We confirm that the sample follows a very tight ``red-sequence'' that does not appear to depend on 
    environment (see \S XX). 
    Appendix~\ref{app:sed} describes the outputs from our SED fitting process 
    (average stellar age, metallicity, and internal dust extinction). 
    We do not utilize these quantities in this paper, but we have checked that they all 
    behave reasonably for both samples. 
    As expected, the integration of the 1-D profile out to very large radius recovers 
    more luminosity (stellar mass) compared to the \cmodel{}-based estimates. 
    This will be shown in Section \ref{ssec:s82}.

    Our methodology ignores any radial variations in \m2l{}. 
    It is well known that massive ETGs have negative optical color gradients indicating 
    gradients in \m2l{} (e.g.\ \citealt{LaBarbera2012}; 
    \citealt{DSouza2015}). \jenny{earlier reference here?}
    These color gradients are shallow and smooth out to a few times the effective 
    radius and color gradients at the outskirts are not yet well quantified.
    Our results looking at the outer envelopes as a function of mass and environment 
    will be robust as long as there is \emph{no significant difference in 
    the average color gradient between sub-samples}.
    %More importantly, for the comparison between the \rbcg{} and \nbcg{} samples, 
    %our results will be robust as long as there is \emph{no significant difference in 
    %the average color gradient between the two samples}. 
    We have confirmed that this is indeed the case (see Section~\ref{ssec:ell_color}).

>>>>

% Package Settings
\hypersetup{colorlinks=true,
            citecolor=MidnightBlue,
            linkcolor=MidnightBlue,
            filecolor=magenta,      
            urlcolor=cyan}
\urlstyle{same}

@@

% Commenting:
\newcommand{\xxx}[1]{\textcolor{red}{\textbf{XXX}}}
\newcommand{\todo}[1]{\textcolor{red}{\textbf{TODO:~#1}}}
\newcommand{\plan}[1]{\textcolor{cyan}{#1}}
\newcommand{\addref}{{\textcolor{red}{REF}}}
\newcommand{\note}[2]{\textcolor{blue}{\textbf{[Comment (#1): #2]}}}
\newcommand{\song}[1]{\textcolor{magenta}{\textbf{[Song: #1]}}}
\newcommand{\alexie}[1]{\textcolor{blue}{\textbf{[Alexie: #1]}}}
\newcommand{\jenny}[1]{\textcolor{Bittersweet}{\textbf{[Jenny: #1]}}}
\newcommand{\kevin}[1]{\textcolor{green}{\textbf{[Kevin: #1]}}}
\newcommand{\update}[1]{\textcolor{PineGreen}{#1}}
%\newcommand{\update}[1]{#1}

@@

    For the remainder of this paper, we will use \mtot{} as a proxy of ``total'' 
    stellar mass. 
    \update{
    As expected, the integration of the 1-D profile out to very large radius recovers 
    more luminosity (stellar mass) compared to the \cmodel{}-based estimates 
    (Fig \ref{fig:mass_diff}).
    }
    \song{Work in progress.}

    In Appendix~\ref{app:sed}, we briefly summarize the basic statistics of 
    the sample using our estimates of \mtot{} and \minn{}.
    We confirm that the sample follows a very tight ``red-sequence'' that does not appear to depend on 
    environment (see \S XX). 
    Appendix~\ref{app:sed} describes the outputs from our SED fitting process 
    (average stellar age, metallicity, and internal dust extinction). 
    We do not utilize these quantities in this paper, but we have checked that they all 
    behave reasonably for both samples.

    \song{The color gradients and ellipticity profiles will be updated}
    Our methodology ignores any radial variations in \m2l{}. 
    It is well known that massive ETGs have negative optical color gradients indicating 
    gradients in \m2l{} (e.g.\ \citealt{LaBarbera2012}; 
    \citealt{DSouza2015}). \jenny{earlier reference here?}
    These color gradients are shallow and smooth out to a few times the effective 
    radius and color gradients at the outskirts are not yet well quantified.
    Our results looking at the outer envelopes as a function of mass and environment 
    will be robust as long as there is \emph{no significant difference in 
    the average color gradient between sub-samples}.
    %More importantly, for the comparison between the \rbcg{} and \nbcg{} samples, 
    %our results will be robust as long as there is \emph{no significant difference in 
    %the average color gradient between the two samples}. 
    We have confirmed that this is indeed the case (see Section~\ref{ssec:ell_color}).
